
\documentclass[letterpaper,11pt]{article}

\usepackage{lmodern}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{{marvosym}}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\fancyfoot[L]{Rathika - Resume}

\begin{document}

%----------HEADING----------

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
{\fontsize{22}{24}\selectfont\textbf{Rathika S}} & +91 9080053414 \\
\href{https://github.com/radik-ha}{https://github.com/radik-ha} &
\href{mailto: rathikaari10@gmail.com}{rathikaari10@gmail.com}
\end{tabular*}
\vspace{4pt}

\vspace{8pt}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Einstein College of Engineering}{Tirunelveli, India}
      {B.E., Computer Science and Engineering}{2024-2028}
     
    \resumeSubheading
      {Government Hr. Sec. School}{Tenkasi, India}
      {Higher Secondary School Examination (Score: 86.4\%)}{2024}
      
  \resumeSubHeadingListEnd

\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, C} \\
      \vspace{4pt}
     \textbf{Web Development Frameworks}{: HTML, CSS, JavaScript, ReactJS, Bootstrap} \\
      \vspace{4pt}
     \textbf{Version Control Systems}{: Git, GitHub}
    }}
 \end{itemize}

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{RAG Assistant} $|$ \emph{Python, FAISS, SentenceTransformers, Google Gemini API}}
          
         \resumeItemListStart
            \resumeItem{Developed a Retrieval-Augmented Generation (RAG) system to process scientific text and generate context-aware comprehension questions.}
            \resumeItem{Implemented FAISS for fast and efficient vector similarity search over large document embeddings.}
            \resumeItem{Used SentenceTransformer to convert raw text into dense semantic embeddings for accurate information retrieval.}
            \resumeItem{Integrated Gemini (Google Generative AI) to generate high-quality, context-aware questions from retrieved content.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Crud Page} $|$ \emph{HTML, CSS, JavaScript}}
          
          \resumeItemListStart
            \resumeItem{Developed a CRUD web application for managing user records.}
            \resumeItem{Implemented Create, Read, Update, and Delete operations using JavaScript.}
            \resumeItem{Designed a responsive and user-friendly interface.}
            \resumeItem{Applied form validation to ensure data accuracy.}
            \resumeItem{Enhanced user experience through dynamic content updates.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{WhatsApp UI Clone} $|$ \emph{ReactJS}}
          
          \resumeItemListStart
            \resumeItem{Developed a WhatsApp-inspired messaging interface using ReactJS.}
            \resumeItem{Implemented conditional rendering for dynamic UI updates.}
            \resumeItem{Created reusable React components for better maintainability.}
            \resumeItem{Designed a responsive layout compatible with multiple devices.}
            \resumeItem{Improved front-end development skills through component-based architecture.}
          \resumeItemListEnd
       \resumeProjectHeading
          {\textbf{Zacebook} $|$ \emph{ReactJS}}
        
          \resumeItemListStart
            \resumeItem{Built a social media-inspired application using ReactJS.}
            \resumeItem{Utilized Props and useState for component communication and state management.}
            \resumeItem{Created reusable UI components for scalability.}
            \resumeItem{Implemented interactive features to enhance user engagement.}
            \resumeItem{Applied React best practices for maintainable code.}
          \resumeItemListEnd
        \resumeProjectHeading
          {\textbf{Animals Sound} $|$ \emph{HTML, CSS, JavaScript}}
          
          \resumeItemListStart
            \resumeItem{Developed an interactive application that plays animal sounds on user interaction.}
            \resumeItem{Implemented JavaScript event handling for audio playback.}
            \resumeItem{Designed an engaging and responsive user interface.}
            \resumeItem{Enhanced user experience through interactive functionality.}
            \resumeItem{Demonstrated DOM manipulation and multimedia integration skills.}
          \resumeItemListEnd
          \vspace{60pt}
        \resumeProjectHeading
          {\textbf{Web Piano} $|$ \emph{HTML, CSS, JavaScript}}
          
          \resumeItemListStart
            \resumeItem{Built a virtual piano application capable of generating musical notes.}
            \resumeItem{Implemented keyboard and mouse-based interactions.}
            \resumeItem{Integrated audio playback using JavaScript.}
            \resumeItem{Designed an intuitive and responsive interface.}
            \resumeItem{Applied event-driven programming concepts for real-time interaction.}
          \resumeItemListEnd
           
        \resumeProjectHeading
          {\textbf{My First React App} $|$ \emph{ReactJS}}

          \resumeItemListStart
            \resumeItem{Developed a beginner-friendly React application to understand component-based development.}
            \resumeItem{Implemented reusable React components and basic state management to create an interactive user interface.}
          \resumeItemListEnd
              
        \resumeProjectHeading
          {\textbf{Fruits Page} $|$ \emph{HTML, CSS}}

          \resumeItemListStart
            \resumeItem{Developed a responsive webpage showcasing fruits using Flexbox and Flex-Wrap layouts.}
          \resumeItemListEnd
        \resumeProjectHeading
          {\textbf{Vegetables Page} $|$ \emph{HTML, CSS}}
          
          \resumeItemListStart
            \resumeItem{Created a responsive website displaying vegetable information using modern CSS Flexbox techniques.}
          \resumeItemListEnd
        \resumeProjectHeading
          {\textbf{Virus Page} $|$ \emph{Bootstrap}}
       
          \resumeItemListStart
            \resumeItem{Built an informative and responsive webpage using Bootstrap components and grid systems.}
          \resumeItemListEnd
        \resumeProjectHeading
          {\textbf{Dolphin Page} $|$ \emph{HTML, CSS}}
     
          \resumeItemListStart
            \resumeItem{Designed a visually appealing webpage presenting information about dolphins.}
          \resumeItemListEnd
        \resumeProjectHeading
          {\textbf{Green Calculator} $|$ \emph{HTML, CSS, JavaScript}}
        
          \resumeItemListStart
            \resumeItem{Developed a web-based calculator capable of performing basic arithmetic operations.}
          \resumeItemListEnd
        \resumeProjectHeading
          {\textbf{Insects Page} $|$ \emph{HTML, CSS  (Media Query)}}
        
          \resumeItemListStart
            \resumeItem{Created a responsive website showcasing insect information using CSS media queries..}
          \resumeItemListEnd
      
    \resumeSubHeadingListEnd

    
\section{Achievements/Activities}
\begin{itemize}[leftmargin=0.15in]

\item \textbf{Tamil Talent Search Examination (TTSE) Scholarship Recipient} \\
Qualified in the Tamil Talent Search Examination (TTSE) conducted by the Government of Tamil Nadu at the district level during 11th standard. Selected for a merit-based scholarship in recognition of academic excellence and strong aptitude.
\item \textbf{Error Hunt Competition – Triogenix'26 Technical Symposium} \\
Participated in the Error Hunt competition held as part of Triogenix'26 Technical Symposium at Thamirabharani Engineering College, Tirunelveli (MAR 2026). Gained hands-on experience in debugging and problem-solving by identifying and correcting programming errors.
\item \textbf{LLM-Based Chatbot – National Level Technical Symposium, P.S.R. Engineering College, Sivakasi} \\
Presented and developed an AI-powered chatbot project using Large Language Model (LLM) concepts at a National Level Technical Symposium. The chatbot is designed to understand natural language queries and generate intelligent, human-like responses. It improves user interaction by providing context-aware answers and simulating conversational AI behavior. The project demonstrates the application of modern AI techniques in real-time communication systems and enhances automation in information retrieval. (SEP 2025)
\item \textbf{Painting Competition – Kalaithiruvizha (Government of Tamil Nadu)} \\
Selected for district-level participation in a painting competition conducted under Kalaithiruvizha by the Government of Tamil Nadu. The event was held at Kongunadu Engineering College, Trichy, and showcased creative and artistic abilities through visual expression.(2023 - 2024)
\item \textbf{SoloLearn Certifications} \\
Completed 9 certifications from SoloLearn covering programming and web development, including HTML, CSS, JavaScript, Python (beginner to intermediate), Web Development, Python Developer, JavaScript Intermediate, and C Programming. Strengthened core skills in programming fundamentals and web technologies through hands-on practice.
\vspace{60pt}
\end{itemize}
\end{document}